\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-16 trunk/europa.tex
smoother transition into the "europa architecture" section.

>>>>

\eu is implemented as a library that encapsulates all the elements described above and makes them easily accessible through modeling and API layers.
A user will typically use the modeling facilities to inject a problem domain description, and the API to extract and manipulate plans, and to obtain information about plan flaws and constraint violations at any stage of the planning process.
